Acceleration of plague outbreaks in the second pandemic

### 2020-08-28 supp.Rnw
Wills and Testaments hyperlink to ms.pdf
insert DOI and get fix footnote hypertarget

\documentclass[9pt,twocolumn,twoside,lineno,table]{pnas-new}
% Use the lineno option to display guide line numbers if required.

@@

\definecolor[named]{verylightgray}{rgb}{0.93,0.93,0.93}

@@

\author{David J.\,D.\ Earn, Junling Ma, Hendrik Poinar, Jonathan Dushoff, Benjamin M.\ Bolker}
\correspondingauthor{E-mail: \texttt{earn@math.mcmaster.ca}}

@@

The Calendar of Wills probated in the Court of Husting \cite{Shar1889} is organized by court dates, so every will is associated with a definite date on which it was probated; in contrast, only 64\% of the wills provide information on the date of writing \cite{Bush19}. Despite this lower sample size and the fact that wills were in some cases written long before death, dates of writing actually provide a much more plausible representation of the epidemic patterns in the 14th century than probate dates (\cref{F:willsVSprobates}).  Graphs in the main text (\cref{F:plot3sources,F:timeseries,F:combdata}) are based on counts of wills written.  See \hyperlink{mainsec:Data.wills}{``Wills and testaments''} in the Data section of the main text for further discussion.

@@

Cummins \emph{et al.} \cite{Cumm+16} obtained parish register data from \href{https://www.ancestry.com}{ancestry.com} and have made the weekly counts of deaths available at \url{http://neilcummins.com}.  For the 16th and 17th century epidemics, the parish data provide a third source.  For 1593, these are the only reliable data (we consider them to be reliable because they are part of a continuous weekly time series from 1538 onwards).

@@

With this approach we failed to achieve good (convergent) fits for only three combinations of source and outbreak year, all for minor outbreaks (London bills for 1578 and 1582, Canterbury wills for 1581); these cases are excluded from the tables and figures shown below.

>>>>

\documentclass[9pt,twocolumn,twoside,lineno,table]{pnas-new}
% Use the lineno option to display guide line numbers if required.
\definecolor[named]{verylightgray}{rgb}{0.93,0.93,0.93}
\renewcommand{\linenumberfont}{\normalfont\sffamily\tiny\color{lightgray}}
\urlstyle{tt}

@@

@@

\author{David J.\,D.\ Earn, Junling Ma, Hendrik Poinar, Jonathan Dushoff, Benjamin M.\ Bolker}
\correspondingauthor{E-mail: {\color{blue}\texttt{earn@math.mcmaster.ca}}
  \\\bigskip DOI: \texttt{10.1073/pnas.2004904}
}

@@

The Calendar of Wills probated in the Court of Husting \cite{Shar1889} is organized by court dates, so every will is associated with a definite date on which it was probated; in contrast, only 64\% of the wills provide information on the date of writing \cite{Bush19}. Despite this lower sample size and the fact that wills were in some cases written long before death, dates of writing actually provide a much more plausible representation of the epidemic patterns in the 14th century than probate dates (\cref{F:willsVSprobates}).  Graphs in the main text (\cref{F:plot3sources,F:timeseries,F:combdata}) are based on counts of wills written.  See \href[page=2]{ms.pdf}{``Wills and testaments''} in the Data section of the main text for further discussion.

@@

Cummins \emph{et al.} \cite{Cumm+16} obtained parish register data from \href{https://www.ancestry.com}{\texttt{ancestry.com}} and have made the weekly counts of deaths available at \url{http://neilcummins.com}.  For the 16th and 17th century epidemics, the parish data provide a third source.  For 1593, these are the only reliable data (we consider them to be reliable because they are part of a continuous weekly time series from 1538 onwards).

@@

With this approach we failed to achieve good (convergent) fits for only three combinations of source and outbreak year, all for minor outbreaks (London bills for 1578 and 1582, Canterbury wills for 1581); these cases are excluded from the tables and figures shown below.
%% hack this target because pnas style breaks footnote hyperrefs:
\hypertarget{Hfootnote.1}{}
